\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{fontspec}

\begin{document}

\part{Adnan Utayim}

% Removed Personal Profile Section
\iffalse
\section{Profile}
$\bullet$ 5 years of academic programming experience. \\
$\bullet$ Keen attention to details and exemplary organization skills.\\
$\bullet$ Team player with a passion to learn and contribute.\\
$\bullet$ Aptitude for solving challenging problems.\\
$\bullet$ Open to developmental feedback to help hone knowledge and skills. \\
$\bullet$ Multiple academic distinctions and awards.
\fi


    

\section{Experience}
\begin{eventlist}

\item{2017 -- 2018}
     {Concordia University}
     {Research Associate}

$\bullet$ Immersive and Creative Technologies Laboratory.\\
$\bullet$ 3D Reconstruction of large-scale areas from remote-sensor data.\\
$\bullet$ Inversed Raytracing for illumination-reversal using CUDA.



\item{2016 -- 2017}
     {American University of Beirut}
     {Research Assistant}

$\bullet$ Coauthored a research paper on Partially Asynchronous Interactions in HDBIP.\\
$\bullet$ A framework for automated distributed implementation of component-based models. \\
    $\bullet$ Published in iFM 2018. 

\item{2016 -- 2017}
     {Interactive Life}
     {Android Developer}

$\bullet$ Development and maintenance of an Android SDK.\\
$\bullet$ Enables building complete mobile applications corresponding to user-defined drag and drop design.

\item{2015 -- 2016}
     {American University of Beirut}
     {Private Tutor}

$\bullet$ $60^+$ hours of tutoring university students.\\
$\bullet$ Courses related to Algorithms, Data Structures, and Theoretical Computing.

\item{2015 -- 2016}
     {American University of Beirut}
     {System Analyst Assistant}

$\bullet$ Work and Study Program.\\
$\bullet$ Handling and maintaining a network of over 100 workstations running different operating systems. \\
$\bullet$ Providing technical support for academic units.


\end{eventlist}


\section{Technical Skills}

    {\textbf{Advanced}\break
    Java, C++, Algorithms, Data Structures, Android, OpenGL, Linux, \LaTeX, Vim, Git, Linear Algebra, Number Theory, Computer Graphics.
    \hfill\break


    \textbf{Intermediate}\break
    C, C\#, Unity, Computer Vision,  Cuda, Bash Scripting, MySQL, CMake, Makefile Utility, MPI, OpenMP.
    \hfill\break

    \textbf{Begginer}\break
    LISP, Prolog, Ruby, AspectJ, Python, Omnet++, Docker}


\personal
    {400, rue Lansdowne. App. 213\hfill\break 
     Saint-Bruno-de-Montarville (QC) J3V 1X3\hfill\break
    Canada}
    {+1(438) 863-5468}
    {a.utayim@gmail.com}
    
    
    
\section{\break Publications}
{Salwa Kobeissi, Adnan Utayim, Mohamad Jaber, Yliès Falcone.  Facilitating the Implementation of Distributed Systems with Heterogeneous Interactions. IFM, Sep 2018, Maynooth, Ireland. 
\href{https://link.springer.com/chapter/10.1007/978-3-319-98938-9_15?fbclid=IwAR3mB_0l1FImySHqTeFfwwBxNwwAB3lfXOTerruuuzMAQN9nHZKYdGKVSzk}{\textbf{Read online}}




\section{\break Education}
\begin{factlist}

\item{2017 - Pres}
    {\textbf{Concordia University}\hfill\break
      B.Sc. Computer Science.\hfill\break
      Transfer Student.\hfill\break 
      GPA: 3.5 \hfill\break
      Graduating May 2020.
     }

\item{2014 - 2016}
    {\textbf{American University of Beirut}\hfill\break
     B.Sc. Computer Science. \hfill\break
     GPA: 3.7 \hfill\break
     Enrolled for three semester.}


\end{factlist}    




\section{Distinctions \& Awards}
\begin{factlist}
   
\item{2018}
    {\textbf{NSERC Research Award}\hfill\break
    Awarded by the Natural Sciences and Engineering Research Council of Canada.
    }


\item{2016}
    {\textbf{Supernacci Competition}\hfill\break
     $2^{nd}$ place. An algorithmic-math competition held annually in the American University of Beirut.} 
\item{2015}
    {\textbf{ACM LCPC}\hfill\break
     $1^{st}$ place and Fierce Programmers. Lebanese Collegiate Programming Contest.}
\item{2015}
    {\textbf{Student of the Year}\hfill\break
     Awarded by the American University of Beirut for outstanding academic performance in the department of computer science.}
\item{2015}
    {\textbf{Dean's Honor List}\hfill\break
     American University of Beirut. For achieving the highest GPA in the Department of Computer Science.}


\end{factlist}



\end{document}
