\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{fontspec}

\begin{document}

\part{Adnan Utayim}



\section{Profile}
$\bullet$ 5 years of academic programming experience. \\
$\bullet$ Keen attention to details and exemplary organization skills.\\
$\bullet$ Team player with a passion to learn and contribute.\\
$\bullet$ Aptitude for solving challenging problems.\\
$\bullet$ Open to developmental feedback to help hone knowledge and skills. \\
$\bullet$ Multiple academic distinctions and awards.




\section{Experience}
\begin{eventlist}

\item{2017 -- 2018}
     {Concordia University}
     {Research Associate}

$\bullet$ Immersive and Creative Technologies Laboratory.\\
$\bullet$ Working on multiple research topics on Computer Graphics and Computer Vision.\\
$\bullet$ 3D Reconstruction of large-scale areas from remote-sensor data.\\
$\bullet$ Inversed Raytracing for illumination-reversal using CUDA.



\item{2016 -- 2017}
     {American University of Beirut}
     {Research Assistant}

$\bullet$ Coauthored a research paper on Partially Asynchronous Interactions in $BIP^+$.\\
$\bullet$ A framework for automated distributed implementation of component-based models. \\
    $\bullet$ Published in IFM 2018. 

\item{2016 -- 2017}
     {Interactive Life}
     {Android Developer}

$\bullet$ Development and maintenance of an Android SDK.\\
$\bullet$ Enables building complete mobile applications corresponding to user-defined drag and drop design.

\item{2015 -- 2016}
     {American University of Beirut}
     {Private Tutor}

$\bullet$ $60^+$ hours of tutoring university students.\\
$\bullet$ Courses related to Programming, Data structure, Algorithms, and Theoretical Computing.

\item{2015 -- 2016}
     {American University of Beirut}
     {System Analyst Assistant}

$\bullet$ Work and Study Program.\\
$\bullet$ Handling and maintaining a network of over 100 workstations running different operating systems. \\
$\bullet$ Providing technical support for academic units.


\end{eventlist}



\personal
    {213 - 400,  Rue Lansdowne, Saint Bruno \hspace{1cm} Qc J3V 1X3}
    {(438) 863-5468}
    {mmu00@mail.aub.edu}
    
\section{Computer Skills}

\begin{factlist}

\item{Advanced}
     {C++, Java, Android, Linux, Computer Graphics, OpenGL, Linux, MPI, OpenMP, \LaTeX, MySQL, Vim, Git}


\item{Intermediate}
     {C\#, Unity, Computer Vision,  Cuda, Bash Scripting, CMake, Makefile Utility}

\end{factlist}    
    

\section{Education}

\begin{yearlist}

\item[Undergrad Student]{2017 -- Pres.}
     {Computer Science } 
     {Concordia University.}

\item[Undergraduate Student]{2014 -- 2016}
     {Computer Science} 
     {American University of Beirut. Enrolled for three semesters.}



\end{yearlist}



\section{Achivements and Awards}

\begin{yearlist}

\item{2018}
     {NSERC Research Award}
     {Awarded by the Natural Sciences and Engineering Research Council of Canada}


\item{2016}
     {Supernacci Competition}
     {$2^{nd}$ place. An algorithmic-math competition held annually in the American University of Beirut.} 
\item{2015}
     {ACM LCPC}
     {$1^{st}$ place and Fierce Programmers. Lebanese Collegiate Programming Contest, an international programming competition.}

\item{2015}
     {Student of the Year}
     {Awarded by the American University of Beirut for outstanding academic performance in the department of computer science.}

\item{2015}
     {Dean's Honor List}
     {American University of Beirut. For achieving the highest GPA in the Department of Computer Science}

\end{yearlist}

    
\section{Publications}
\textbf{Facilitating the Implementation of Distributed Systems with Heterogeneous Interactions.} Salwa Kobeissi, Adnan Utayim, Mohamad Jaber, Yliès Falcone. IFM 2018 - 14th International Conference on integrated Formal Methods, Sep 2018, Maynooth, Ireland. pp.1-19. \href{https://link.springer.com/chapter/10.1007/978-3-319-98938-9_15?fbclid=IwAR3mB_0l1FImySHqTeFfwwBxNwwAB3lfXOTerruuuzMAQN9nHZKYdGKVSzk}{Read Online}





\end{document}
